\textbf{Instructions}

\begin{itemize}
\item This homework has two parts: Q1 and Q2 are written questions and Q3 is a programming assignment with some written questions. Each part needs to be submitted as follows:
    \begin{itemize}
        \item Submit the answers to the written questions as a \texttt{pdf} file on Canvas for the assignment corresponding to Homework 4 Written. 
        This should contain the written answers to Q1 and Q2. Name the pdf file as \texttt{LastName\_FirstName.pdf}. 
        We recommend students type answers with LaTeX or word processors for this part. 
        A scanned handwritten copy would also be accepted, try to be clear as much as possible. 
        No credit may be given to unreadable handwriting. 
        \item The programming assignment requires you to work on boilerplate code and text data, which are provided in a zip file on Canvas. 
        Submit the code to the programming assignment in a zip that contains (1) \texttt{POS\_tagging.ipynb}, which will contain both the code \textbf{and the written answers to Q3}, and (2) a PDF version of the notebook \texttt{POS\_tagging.pdf}.
        You can convert the notebook to a PDF by clicking ``File'' $\xrightarrow{}$ ``Download as'' $\xrightarrow{}$ ``PDF.'' \\
        This submission is to be made on Canvas for the assignment corresponding to Homework 4 Programming. 
        Name the zip file as \texttt{LastName\_FirstName.zip}.
        
        \item You can also submit output files to Gradescope ``HW4 POS Tagging'' to check your models' performance.
        The uploaded file \texttt{test\_labels.txt} should contain the predicted tags from your POS tagger.
        You can see your score for Q3 programming questions as soon as you submit it.
    \end{itemize}

    \item For the written questions, write out all steps required to find the solutions so that partial credit may be awarded.
    \item We generally encourage collaboration with other students. 
    You may discuss the questions and potential directions for solving them with another student. 
    However, you need to write your own solutions and code separately, and not as a group activity. 
    Please list the students with whom you collaborated.
\end{itemize}